Modelling potential environmental impacts of science activity in Antarctica

### 2025-09-24 talk/index.qmd
final edits to talk
some final tweaks to slides

## [Conclusions]{style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"} {background-image="beacon-valley.jpg" style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"}
### Terrain-differentiated data-fitted hiking functions are a novelty
### Potential wider application of radius-limited betweenness centrality?

&nbsp;

#### For more
* On this project: [[dosull.github.io/antarctica](https://dosull.github.io/antarctica)]{style="background-color:rgba(102,0,0,0.65);"}

* About ![](logo.png){style="vertical-align:middle;width:60px"} [Geospatial Stuff: [dosull.github.io](https://dosull.github.io)]{style="background-color:rgba(102,0,0,0.65);"}

@@

# {background-image="background-image.png"}
[Questions?]{style="font-size:200px;color:black;opacity:25%;text-align:center;"}

>>>>

## [Conclusions]{style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"} {background-image="beacon-valley.jpg" style="text-shadow:0px 0px 8px rgba(102,0,0,0.5);"}
### Terrain-differentiated data-fitted hiking functions are a novelty
### Potential wider application of radius-limited betweenness centrality?
### Manuscript in preparation

@@

# {background-image="background-image.png"}

### Questions? {style="font-size:200px;color:black;opacity:25%;text-align:center;font-weight:700;"}

::: {style="background-color:rgba(102,0,0,0.1);"}
<h2 style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);">For more</h2>
### On this project: [dosull.github.io/antarctica](https://dosull.github.io/antarctica) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
### About ![](logo.png){style="vertical-align:middle;width:60px;text-align:center;"} Geospatial Stuff: [dosull.github.io](https://dosull.github.io) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
:::
